---
title: "Lucas_Lab_4"
author: "Lucas Brack"
date: "February 6, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = `bwt/oz`) #renaming `bwt/oz` because the "/" sign requires special care
babies<- na.omit(babies)
```

#Team part question 2 plot
```{r}
ggplot(data=babies, aes(x=gestation, y=bwtoz, fill=as.factor(smoke)))+
  geom_boxplot()+
  labs(title =" Smoking decreases Babies' Birth Weight", x = "Gestation (Days)", y = "Birth Weight (oz)")+
  scale_fill_discrete(name="", labels = c("Mother Doesn't Smoke", "Mother Does Smoke"))
```



#Lucas Brack individual
How does education and age effect the number of pregenancies a woman has had?
```{r}
ggplot(data=babies, aes(x=mage, y=parity, color=as.factor(med)))+
  geom_point(position='jitter')+
  geom_smooth(method='lm', se=FALSE)+
  labs(title ="Number of Pregencies Goes Down as Education Increases", x = "Mother's Age", y = "Number of Times Pregnant")+
  theme_dark()+
  scale_color_discrete(name="Mother's Education Level")+
scale_color_manual(labels = c("Less than 8th grade", "8th to 12th grade. Did not graduate high school","High school graduate, no other schooling", "High school graduate + trade school", "High school graduate + some college", "College graduate", "Trade school but unclear if graduated from high school" ),values = c("blue", "red", "green", "orange", "cyan", "pink", "yellow"))


```

I choose to do this because I wanted to see the difference in education had in pregenancy. I did this by making a scatter point graph, color coded for each education level, and puting the line of best fit on it. I did this so I could see the difference in them. the graph showed me that less educated women have more pregenancies, and that they have them more consistently through out their life. College educated women have less kids, and over a shorter period of time.
